### 2019-12-17 tex/ms.tex
more

% could take out GUIDE cameras from this table...

@@

\section{Input GFA On-sky Data}

@@

\begin{itemize}
\item They were taken during a photometric time period.
\item They were taken in reasonably good seeing -- the FWHM is typically
\item They are taken in a region of high source density
\item They are relatively long GFA exposures (the unique exposure times are 30 seconds and 60 seconds), further improving the density of well-detected sources.
\item Very close to airmass = 1, minimizing impact of any errors in atmospheric transmission component of GFA throughput prediction.
\item All six cameras worth of guide GFA images are available for all exposures in this sequence.
\item The exposures were dithered at a scale of $\sim$30$''$ per coordinate, so that we are not always sampling the same stars at the same GFA pixel locations during ever single exposure.
\end{itemize}

@@

% mention PSF-based Aperture Correction

% maybe show an example PSF image?

@@

@@

% first appendix
% confirming GFA exptime with star trails

% second appendix all of the per-camera per-amp scatter plots of GFA sources

@@

Appended below is the full set of per-exposure, per-camera, per-amp scatter plots of GFA instrumental magnitudes versus PS1 $r$ band AB magnitudes for the set of exposures used during this study.

>>>>

% could take out FOCUS cameras from this table...

@@

\section{Input GFA On-sky Data}
\label{sec:input_data}

@@

\begin{itemize}
\item They were taken during a photometric time period.
\item They were taken in reasonably good seeing -- the FWHM is typically
\item They are taken in a region of high source density. This provides more sources to compare against PS1, better assurance of successful astrometric calibration, and enables good PSF modeling. 
\item They are relatively long GFA exposures (the unique exposure times are 30 seconds and 60 seconds), further improving the density of well-detected sources.
\item Very close to airmass = 1, minimizing impact of any errors in atmospheric transmission component of GFA throughput prediction.
\item All six cameras worth of guide GFA images are available for all exposures in this sequence.
\item The exposures were dithered at a scale of $\sim$30$''$ per coordinate, so that we are not always sampling the same stars at the same GFA pixel locations during ever single exposure.
\end{itemize}

@@

Source detection and astrometric calibration were performed with the \verb|gfa_reduce| GFA off-line reduction package for each camera of each GFA exposure discussed in $\S$\ref{sec:input_data}. Astrometric calibration is necessary in order to identify the correct PS1 match to each GFA detection. Astrometric calibration was successful for all cameras of all exposures. For this study, we perform aperture photometry in a 5 pixel radius circular (in pixel space) aperture. We then correct this aperture photometry to be as close as possible to ``total light''. This is accomplished by first building a PSF model for each guide camera of each GFA exposure, then using this PSF model to compute an aperture correction from the 5 pixel radius aperture to total light within the full extent of the PSF model, then multiplying the aperture photometry by this aperture correction factor. Each PSF model is 61 pixels on a side. The fluxes are measured in raw ADU so as to avoid baking in a specific flat field correction, given that different people may use different flat field corrections and/or that the master flat could evolve over time as more calibration data are obtained.

The per-exposure catalogs have been concatenated and uploaded as a supplementary file \verb|filename.fits|. The aperture fluxes in raw ADU are in the column named COUNTS\_PER\_SECOND and the aperture correction factor is in a column named APCORR\_FAC.

@@

Since the sky location being considered is in the Galactic plane and the comparison sources being used are not especially faint, we assume that all matched sources are pointlike stars rather than extended galaxies. The version of the PS1 catalog being used (`fitscat\_qz\_trim') was also constructed with a star-galaxy separation metric cut meant to retain only stars, further indicating the lack of a need for attempting to make source morphology corrections.

@@

@@

Appended below is the full set of per-exposure, per-camera, per-amp scatter plots of GFA instrumental magnitudes versus PS1 $r$ band AB magnitudes for the set of exposures used during this study. The vertical yellow line indicates the magnitude threshold fainter than which it was considered safe from potential saturation/nonlinearity to use the GFA magnitudes. In each case the red line is fixed to have a slope of unity (the slope is not fit as a free parameter), and the y axis offset is set to the median of the difference between the PS1 AB magnitudes and the instrumental magnitudes for (sufficiently faint) matched sources.
